### 2015-07-06 narrative/evaluation.tex
e
resized the table

\hline
	{\bf Principle/Metric}                   & {\bf User perspective metric}                     & {\bf System perspective metric }\\ \hline
	{\bf Knowledge-centric system} & More knowledge = faster access            &  More knowledge = better resource\\
                                                               &    to higher quality data                               &    utilization across the entire hierarchy \\ \hline

        {\bf Predictable Performance/Accuracy} & More predictability =                     &  Accuracy of the time bounds across \\
                                                                             & better quality of data                      &  multiple layers of the storage hierarchy \\ 
                                                                             & wrote/read in time constrained\\
                                                                             & situations \\ \hline

>>>>

\hline
	{\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
	{\bf Knowledge-centric}                  & More knowledge = faster access  &  More knowledge = better \\
        {\bf system}                             & to higher quality data          &  resource utilization across \\
                                                 &                                 & the entire hierarchy \\ \hline

        {\bf Predictable Performance} & More predictability =                     &  Accuracy of the time bounds \\
        {\bf Accuracy}                & better quality of data                    &  across multiple layers of the\\
                                      &                                           &  storage hierarchy wrote/read \\ 
                                      &                                           &  in time constrained\\
                                      &                                           &  situations \\ \hline
